Full vector inversion of magnetic microscopy images using Euler deconvolution as a priori information

### 2022-12-19 article_1/Conclusion.tex
Add random function with seeds and change variable names
Delete unused images

\noindent{The test using a simply synthetic sample shows the great capability of the method by retrieving not only the precisely center positions }

>>>>

\noindent{The test using a simple synthetic sample shows the great capability of the method by retrieving not only the precisely center positions, but also retrieve de magnetization directions and intensity even under considerable effect of high frequency noise (15 nT). While the complex synthetic sample data allows observing the applicability of the method developed in real samples that are more complex with varied magnetization directions and intensity, in addition to also taking into account the high and low frequency noise.}

\end{singlespace}

### 2022-12-19 article_1/Result1.tex
Delete unused images

\noindent{The modeled magnetization directions not only generate an average direction coincident with the simulated induced field, but also have relatively small Fisher cones of confidence \citep{Fisher1987} due to their clustering (\cref{fig:ComplexSynthetic3}a). On the other hand, the recovered directions may be more sparse, despite this the mean direction obtained is statically the same as the field modeled inside the 95\% confidence cone (\cref{fig:ComplexSynthetic3}b). If necessary, the data can be filtered according to the highest adjustments obtained with the coefficient of determination (R$^2$). The value of R$^2$ can vary from $-\infty$ to 1, with values closest to 1 corresponding to the best modeling results. Thus, filtering the results obtained with the magnetic inversion with R$^2 \geq 0.7$ we obtain the directions closest to the average and less sparse, maintaining the high reliability result (\cref{fig:ComplexSynthetic3}c).}

\begin{figure}[hbpt]
\centering
\includegraphics[width=1.0\textwidth]{ComplexStereo.png}
\caption{a) The real data models a thin section of rock with particles uniformly magnetized in the average direction of the induced field 45\textdegree/45\textdegree. b) The recovered data, without any type of filtering, are sparse, but statistically generate the same average direction. c) It is still possible to filter only the directions of the magnetic sources with the best fitting determined by the coefficient of determination (e.g., $R^ 2 \geq 0.7$) to ensure better grouping of the directions around the mean value.}
\label{fig:ComplexSynthetic3}
\end{figure}

>>>>

\noindent{The modelled magnetization directions not only generate an average direction coincident with the simulated induced field, but also have relatively small Fisher cones of confidence \citep{Fisher1987} due to their clustering (\cref{fig:ComplexSynthetic3}a). On the other hand, the recovered directions may be more sparse, despite this the mean direction obtained is statically the same as the field modeled inside the 95\% confidence cone (\cref{fig:ComplexSynthetic3}b). If necessary, the data can be filtered according to the highest adjustments obtained with the coefficient of determination (R$^2$). The value of R$^2$ can vary from $-\infty$ to 1, with values closest to 1 corresponding to the best modelling results. Thus, filtering the results obtained with the magnetic inversion with R$^2 \geq 0.9$ we obtain the directions closest to the average and less sparse, maintaining the high reliability result (\cref{fig:ComplexSynthetic3}c).}

\begin{figure}[hbpt]
\centering
\includegraphics[width=1.0\textwidth]{ComplexStereo.png}
\caption{a) The real data models a thin section of rock with particles uniformly magnetized in the average direction of the induced field 45\textdegree/45\textdegree. b) The recovered data, without any type of filtering, are sparse, but statistically generate the same average direction. c) It is still possible to filter only the directions of the magnetic sources with the best fitting determined by the coefficient of determination ($R^ 2 \geq 0.9$) to ensure better grouping of the directions around the mean value.}
\label{fig:ComplexSynthetic3}
\end{figure}

### 2022-12-19 article_1/solution_par_table.tex
Delete unused images

\begin{table}[htbp]
\caption{Positioning and magnetization parameters recovered with the inversion.}
\label{tab:InversionTab}
\resizebox{1.0\textwidth}{!}{
\begin{tabular}{ccccccc}
\hline   
\rowcolor[HTML]{FFFFFF} 
\cellcolor[HTML]{FFFFFF}                         & \multicolumn{3}{c}{\cellcolor[HTML]{FFFFFF}Center coordinates}                    & \multicolumn{3}{c}{\cellcolor[HTML]{FFFFFF}Magnetization}     \\
\rowcolor[HTML]{FFFFFF} 
\multirow{-2}{*}{\cellcolor[HTML]{FFFFFF}Sphere} & Xc ($\mu m$) & Yc ($\mu m$) & Zc ($\mu m$) & m ($A \cdot m^2$) & D (\textdegree) & I (\textdegree) \\  \hline   
1                                                & 250.07           & 250.04           & 5.36           & 8.83e-15  $\pm$  2.32e-17           & -140.03  $\pm$  0.18           & -29.45  $\pm$  0.13           \\
\rowcolor[HTML]{FFFFFF} 
2                                                & 500.00           & 500.01           & 7.71           & 7.57e-15  $\pm$  2.91e-17           & 0.23  $\pm$  0.60           & 61.79  $\pm$  0.27           \\
3                                                & 749.92           & 749.98           & 8.38           & 6.10e-15  $\pm$  3.46e-17           & -69.93  $\pm$  0.61           & -50.50  $\pm$  0.35           \\
\rowcolor[HTML]{FFFFFF} 
4                                                & 199.94           & 800.21           & 10.10           & 6.78e-15  $\pm$  5.09e-17           & 125.09  $\pm$  0.48           & 21.02  $\pm$  0.33           \\ \hline                 
\end{tabular}
}
\end{table}

>>>>

\begin{table}[htbp]
\caption{Positioning and magnetization parameters recovered with the inversion.}
\label{tab:InversionTab}
\resizebox{1.0\textwidth}{!}{
\begin{tabular}{ccccccc}
\hline   
\rowcolor[HTML]{FFFFFF} 
\cellcolor[HTML]{FFFFFF}                         & \multicolumn{3}{c}{\cellcolor[HTML]{FFFFFF}Center coordinates}                    & \multicolumn{3}{c}{\cellcolor[HTML]{FFFFFF}Magnetization}     \\
\rowcolor[HTML]{FFFFFF} 
\multirow{-2}{*}{\cellcolor[HTML]{FFFFFF}Sphere} & Xc ($\mu m$) & Yc ($\mu m$) & Zc ($\mu m$) & m ($A \cdot m^2$) & D (\textdegree) & I (\textdegree) \\  \hline   
1                                                & 250.28           & 250.19           & 5.38           & 8.82e-15  $\pm$  1.39e-17           & -140.22  $\pm$  0.11           & -30.04  $\pm$  0.08           \\
\rowcolor[HTML]{FFFFFF} 
2                                                & 500.46           & 500.50           & 7.77           & 7.67e-15  $\pm$  1.90e-17           & -69.42  $\pm$  0.26           & -49.85  $\pm$  0.15           \\
3                                                & 750.73           & 750.72           & 8.57           & 6.31e-15  $\pm$  1.99e-17           & 9.06  $\pm$  0.50           & 62.34  $\pm$  0.22           \\
\rowcolor[HTML]{FFFFFF} 
4                                                & 200.30           & 800.92           & 10.00           & 4.94e-15  $\pm$  3.01e-17           & 124.63  $\pm$  0.39           & 21.76  $\pm$  0.27           \\ \hline                 
\end{tabular}
}
\end{table}
